Title

### 2018-07-31 thesis/paper/paper.tex
Started single best value

\subsection{One-of (Q21510859)}
The one-of constraint fits in the pattern established by the previous two constraints and disallows certain property-value combinations. With \(A\) the set of allowed values the rules for triple, qualifier and reference are respectively:
\begin{equation*}
\begin{split}
\text{violation\_triple}&(S, I, \text{propertyConstant}, V) \leftarrow \\
&\text{tripleEDB}(S, I, \text{propertyConstant}, V) \wedge \text{unequal}(\{A\}, V)
\end{split}
\end{equation*}
\begin{equation*}
\begin{split}
\text{violation\_qualifier}&(S, \text{propertyConstant}, V) \leftarrow \\
&\text{qualifierEDB}(S, \text{propertyConstant}, V) \wedge \text{unequal}(\{A\}, V)
\end{split}
\end{equation*}
\begin{equation*}
\begin{split}
\text{violation\_reference}&(S, \text{propertyConstant}, V) \leftarrow \\
&\text{referenceEDB}(S, \text{propertyConstant}, V) \wedge \text{unequal}(\{A\}, V)
\end{split}
\end{equation*}

@@

>>>>

\subsection{One-of (Q21510859)}
The one-of constraint fits in the pattern established by the previous two constraints and disallows certain property-value combinations. Inequality is pre-processed between all values of constrained statements. With \(A\) the set of allowed values the rules for triple, qualifier and reference are respectively:
\begin{equation*}
\begin{split}
\text{violation\_triple}&(S, I, \text{propertyConstant}, V) \leftarrow \\
&\text{tripleEDB}(S, I, \text{propertyConstant}, V) \wedge \text{unequal}(\{A\}, V)
\end{split}
\end{equation*}
\begin{equation*}
\begin{split}
\text{violation\_qualifier}&(S, \text{propertyConstant}, V) \leftarrow \\
&\text{qualifierEDB}(S, \text{propertyConstant}, V) \wedge \text{unequal}(\{A\}, V)
\end{split}
\end{equation*}
\begin{equation*}
\begin{split}
\text{violation\_reference}&(S, \text{propertyConstant}, V) \leftarrow \\
&\text{referenceEDB}(S, \text{propertyConstant}, V) \wedge \text{unequal}(\{A\}, V)
\end{split}
\end{equation*}

@@

\subsection{Single best value (Q52060874)}
The single best value constraint limits the number of constrained statements with rank preferred on the same item to one. This means during pre-processing the rank information per triple must be extracted and attached to the statement with the new predicate rank\([2]\) which links the statement ID and the rank. Qualifiers and references are not affected since they do not have ranks. Inequality is established between all constrained statement IDs. For the simple case without separators the rule is:
\todo[inline]{Well, this isn't done.}
